A Failure Detection Model for Data Center Networks\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2016-06-25 SIG Proceedings Template-Jan2015 Zip/paper.tex
write paper

\title{A Failure Detection Model in Data Center Network}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kai Shen\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \email{knshen@sjtu.edu.cn}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
}

@@

\keywords{Failure Detection; Data Center Networks}

\section{Introduction}

\section{Related Works}

\section{Data Center Background}

\section{Failure Detection Model}

\section{Evaluation}

\section{Conclusion and Future Works}

\section{Acknowledgement}

\section{References}

>>>>

\title{A Failure Detection Model for Data Center Networks\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kai Shen\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{knshen@sjtu.edu.cn}
% 2nd. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}
Data center.
The rest of this paper is organized as follows. Section 2 discusses related work,

\section{Related Work}
In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure localization in data center networks.

\subsection{Failure Detectors}
A failure detector(FD) is widely recognized as an oracle to intelligently suspect failed processes \cite{chandra1996unreliable}. The monitored process periodically send heartbeat messages to its detector to prove its liveness.

Chen et al. proposed a FD that provides QoS \cite{chen2002quality}. It estimates the expected arrival time(EAs) of the next heartbeat message according to a slide window storing n most recent arrived messages. EAs determine the deadline that the detector will wait for the next heartbeat before suspecting the monitored process. \textit{Chen FD} can adjust current network condition and set the timeout threshold adaptively by referring to recent heartbeats. Bertier et al. proposed a similar FD \cite{bertier2002implementation}, whereas it uses a dynamic way to compute error margin of \textit{Chen FD}. Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output an accrual failure value at any time which stands for the failure probability of the process.

\subsection{Failure Detection Architecture}
A failure detection architecture aims to provide the service of monitoring nodes in large scale distributed systems in a scalable way. Roughly speaking, there are two kinds of architectures. The first one is hierarchical architecture \cite{felber1999failure}, all the nodes are partitioned into different groups, each group has a leader node. Within a group, the leader node is responsible for monitoring all the nodes. Leader nodes periodically send node status information of his group to other leader nodes. Hierarchical architecture can reduce the number of heartbeat messages effectively, but it exists \textit{Single Point of Failure} problem, when the leader node crashes, it needs to select a new leader.
Another alternative solution is Gossip-Style architecture \cite{van1998gossip}. Each node maintains a list containing the \textit{heartbeat counter} for all the nodes in the system. Every T$_{gossip}$ seconds, each node firstly update \textit{heartbeat counter} of itself and then randomly select another node to send its list to. Upon receiving a message, the node will merge two lists and update each node's \textit{heartbeat counter} with the bigger one. If the \textit{heartbeat counter} does not update after T$_{fail}$ seconds, the node will be marked as crashed. If the \textit{heartbeat counter} does not update after T$_{cleanup}$(T$_{cleanup}$
$\ge$T$_{fail}$) seconds, it will be removed from the list.
\section{Evaluation}

\section{Conclusions}
This paper proposes a failure detector model for data center networks.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This work is partially supported by the National High-Technology Research and Development Program of China under Grant No.2014AA01A301.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
